%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\linespread{0.8}
\makeatletter
\renewcommand{\document}{%
  \ori@document
  \centerline{{\Huge\bfseries Nishanth Hegde}\hfill%
  \begin{minipage}{6cm}
  \raggedleft
  2700 Ellendale Pl, Apt. 307\\
  (213) 572-9510\\
  Email: nishanth@usc.edu\\ 
  LinkedIn: nishanthhegde
  \end{minipage}}\par
}
\makeatother
\usepackage[left=0.5in,top=0.5in,right=0.35in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Southern California, Los Angeles, CA} \hfill {\em August 2018 - June 2020} 
\\ MS in Computer Science (Data Science) \hfill { }  

{\bf PES University, Bangalore, India} \hfill {\em Aug 2014 - May 2018} 
\\ B. Tech in Computer Science \hfill {GPA: 9.05/10 }  



\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{McAfee Software India Pvt. Ltd}{January 2018 - June 2018}{Undergrad Technical Intern}{Bangalore, India}
\item Worked on Adaptive Threat Protection for Enterprise macOS \& Linux devices by enhancing features and testing.
\item Fixed a release blocker bug related to C++ smart pointers and improved code coverage by 20\%. The software was released during my internship.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Microsoft Innovation Lab, PES University}{May 2016 - May 2017}{Research Intern}{Bangalore, India}
\item Developed a standalone real-time speaker recognition system. Prototyped in MATLAB and  in Python. 
\item Arrived at a novel feature set 12 dimensions lesser than state-of-the-art models without significant loss in accuracy.
\item Recruited new interns in my senior year and mentored teams working on machine learning.
\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------
\begin{rSection}{Projects}

%------------------------------------------------

\begin{rSubsection}{Blind Image Deconvolution}{}{}{}
\item Headed a team of three people and worked on blur removal for blurred number plates in CCTV footages using Python, OpenCV and Tensorflow.
\end{rSubsection}
\begin{rSubsection}{Fast and Accurate Face Recognition}{}{}{}
\item Formulated a novel pipeline for face recognition tackling issues with training speeds and accuracy. 
\item Research paper was accepted for publication and oral presentation at Soft Computing for Problem Solving 2017.
\end{rSubsection}
\begin{rSubsection}{mlpack}{}{}{}
\item Contributed to open source library for Fast \& scalable machine learning in C++.  
\end{rSubsection}

\begin{rSubsection}{Classifier Comparison for Prediction of Heart Diseases}{}{}{}
\item Studied and reasoned the effectiveness of classifiers like SVM, KNN, etc for prediction of heart disease in R.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Graph Triangle counting algorithm for GPUs}{}{}{}
\item Parallelized triangle counting algorithm using CUDA for 80\% faster execution on NVidia GPUs.
\end{rSubsection}

\begin{rSubsection}{News Aggregator and Crawler}{}{}{}
\item Developed a website that displays personalized news feed controlled by RSS subscriptions and web crawling.
\item Used HTML, Javascript, Bootstrap, MySQL, PHP, Python (BeautifulSoup).
\end{rSubsection}
\begin{rSubsection}{Online Video Game Distribution Platform}{}{}{}
\item Designed and implemented a web platform for video game distribution. MySQL database with PHP backend.  
\end{rSubsection}

\begin{rSubsection}{Java Music Player with GUI}{}{}{}
\item Programmed a music player with Java and Swing with playback controls and effectively handled race conditions.
\end{rSubsection}
\begin{rSubsection}{Two Pass Assembler}{}{}{}
\item Completed a two pass assembler in C for a custom assembly level language in my freshman year.
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming \& Scripting &  C++, C, Java, Python, MATLAB \\
ML Stack & NumPy, OpenCV, Keras, Tensorflow \\
Web Stack & HTML, CSS, JS, Bootsrap, PHP, MySQL \\
Software \& Tools & CUDA, Git, SVN, Jira \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------

\end{document}
